A self-consistency check for unitary propagation of Hawking quanta

### 2016-10-30 Draft_BH_shells.tex
Update Draft_BH_shells.tex

\begin{itemize}
\item {\bf Classical coherence by tracking geodesics.} The classical mode of a massless field basically has its peaks and nodes following null geodesics.
Thus, instead of actually solving the mode function, we can perform a much simpler calculation to track geodesics.
We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
\footnote{In the geometric limit, the shift in geodesics faithfully represents the shift in wave modes. Away from the geometric limit, the relation between them is more complicated, but one being large still implies that the other is, too.}
\item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
A classical uncertainty can be expressed as deviation from such metric, $\Delta g_{\mu\nu}$. 
There are two major challenges here.
\begin{enumerate}
\item There are many more variables than the double-slit experiment. 
We consider only one particular form of $\Delta g_{\mu\nu}$ in this paper---back-reactions from the presence of extra matter of zero total energy. 
It is simple to calculate and reflects the physcial intuition of vacuum pair fluctuation.
\item The value of $\Delta g_{\mu\nu}$ is gauge dependent. 
By relating it to the presence of extra matter, we can express it as a gauge-invariant local quantity, which is the natural thing to hold fixed in our analysis.
\end{enumerate}
%If we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example. 
%However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that. 
%Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
\item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on renormalization.
\end{itemize}

@@

\begin{figure}[tb]
\begin{center}
\includegraphics[scale = 0.6]{Propertime.pdf}
\caption{The two parts of this diagrams describe two different scenarios. The trajectories of the photon are the lines in orange. The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines. The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$. The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$. Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively. The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
\label{fig-setup}
\end{center}
\end{figure}

After some formal calculations in the {\bf Appendix}, we arrive at this simple expression:
\begin{equation}
\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = 
\left(\sqrt{\frac{r_2-2M}{r_1-2M}}\sqrt{\frac{r_1-2(M-\Delta M)}{r_2-2(M-\Delta M)}}-1\right)~,
\label{eq-result}
\end{equation}
where $r_1$ is the location of the inner shell, $r_2$ is the location of the outer shell, and $\pm\Delta M$ are their individual ADM masses.

@@

As the first step, we set $M=0$ in Eq.~(\ref{eq-result}) to study its meaning in Minkowski space. Assuming that $|r_1-r_2| \equiv \Delta r \ll r_1$ and $\Delta M \ll r_1$, the leading order result becomes
\begin{equation}
\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx - \frac{\Delta M}{r_1^2} \Delta r 
\equiv \sigma \Delta r~.	
\label{eq-Mink}
\end{equation}
This seems to be a reasonable answer. 
First of all, it is quite unlikely that the entire shell of mass $\Delta M$ fluctuates out of vacuum.
It is reasonable that any change to the null geodesics is about a local energy density of the particular piece of shell they happen to pass through.
Secondly, this result is gauge invariant. For an observer at rest, $\sigma$ is the local energy density and $\Delta r$ is the proper distance. 
For a boosted observer, $\sigma$ increases by a boost factor while $\Delta r$ contracts by the same factor.
We take it as a good sign that other forms of geometric uncertainty can also be parametrize by a similar, gauge invariant quantity.

The na\"ive interpretation of Eq.~(\ref{eq-Mink}) is that even in Minkowski space, geometric uncertainty can potentially decohere classical mode functions.
By our definition, that poses some threat to QFT in Minkowski space.
We are going to assume that unitarity in QFT is fine in Minkowski space, effectively ``renormalize away'' the effect of Eq.~(\ref{eq-Mink}).
One can imagine a simple subtraction by a counter term.
Or alternatively, since the actual value of $(\sigma\Delta r)$ is unknown, we assume that it is small enough to not cause any concern.

Next we study Eq.~(\ref{eq-result}) with an actual black hole. 
When the double-shell is very far away from the black hole, $r_1\gg M$, it agrees with Eq.~(\ref{eq-Mink}) as expected. 
The interesting thing here is that when this pair of geodesics originate near the horizon, the double-shell could also be somewhere near the horizon. 
In that limit, Eq.~(\ref{eq-result}) can be approximated by
\begin{equation}
	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.	\label{eq-NearHorizon}
\end{equation}
where $l$ is the proper distance between $r_1$ and the horizon and $\delta l$ is the proper distance between the two shells. 
We can see that the same gauge-invariant quantity in Minkowski space from Eq. (\ref{eq-Mink}) appears in the denominator this time
\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\delta l$.}. We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} = -1$, which is the largest possible effect in the arrival times of two geodesics. However, the small $l$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT. 
After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.

@@

Showing the lack of unitarity in the propagation of Hawking quanta does not resolve all the problems. 
Usually, one pictures a nonunitarity process as losing information. 
In the context of black hole information, a Hawking quantum actually has to {\it recover} information. 
A near-horizon mode starts from a maximally mixed (thermal) state with no information, since its partner is the interior mode that never comes out of the horizon. 
After the non-unitary propagation, such a informationless mode has to become an asymptotic Hawking quantum which carries the information to purify the rest of the Hawking radiation there.
The exact detail of this process remains an enigma.

Since unitarity is lost to the local geometric uncertainty, what restores information must be the interaction with the local geometry.
More precisely, the particular effect of local geometric uncertainty here is to create extra shifts between parallel null geodesics, which is reminiscent of memory effects or supertranslation\cite{GW_memory,HeLys14,KodPen16}.
This naturally echoes the idea that the soft hairs \cite{HawPer16} might encode the black hole information and returns them to the Hawking radiation via an interaction that is beyond the na\"ive local QFT\cite{OsuPag16}. 
Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.

\acknowledgements

We thank XXX for discussions.

@@

\section{Calculation}

@@

\subsubsection{Perturbed spacetime - double shell}

Now we introduce two shells of matter with equal and opposite ADM mass, $-\Delta M$ and $\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}. We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells. In this case the particle's move through two different spacetime regions. Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M-\Delta M$ as shown in the top part of figure \ref{fig-setup}.
\\
\\
As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$. Now we need to find the corresponding coordinate time interval in region $II$, $\delta \hat{t}_1$ (in general we will use hats on top of quantities that are evaluated in region $II$). To do this we simply note that the corresponding proper time at $r_1$, $\delta \tau_1$ must be the same in both regions of spacetime - this is a simple consequence of the IJC. The coordinate time intervals at $r_1$, in the two different regions, are therefore related by

\begin{equation}
	\delta t_1 = \delta t_0 = \left( \frac{1 - \frac{2(M - \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta \hat{t}_1.
\end{equation}

@@

\begin{equation}
	\delta \hat{t}_2 = \delta \hat{t}_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M- \Delta M)}{r_2}} \right) \delta t_2.	\label{7}
\end{equation}

Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \right)^\frac{1}{2}$. Where we have dropped the $\left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$ term since we assume the observer is very far away. $\delta t_e = \delta \bar{\tau_0}$ when the observer is far away therefore we can define a dimensionless quantity that quantifies the change in proper time intervals for consecutive photons in perturbed spacetime case and the unperturbed case,

\begin{equation}
	 \frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M-\Delta M)} \right)^\frac{1}{2} - 1\right).	\label{10}
\end{equation}

This expression is exact in the limit that the observer is far away. By expressing the distances from the horizon as, $r_1  =  2M + \epsilon,  r_2  =  2M + \epsilon + \delta \epsilon$, we can write Eq (\ref{10}) as

\begin{equation}
	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = \left( \left( \frac{\epsilon + \delta \epsilon}{\epsilon} \right)^\frac{1}{2} \left( \frac{\epsilon + 2 \Delta M}{\epsilon + \delta \epsilon + 2\Delta M} \right)^\frac{1}{2} - 1\right). \label{12}
\end{equation}

This shows that when there are no shells, $\Delta M = 0$, there is no change in proper time intervals which is what one would expect. More interestingly we see that there is no $M$ dependence in this equation. This suggests the effect is present in flat space as well. One may interpret this effect as being a phase shift between the photons as the travel through two different gravitational potential wells. Before jumping to any conclusions, however, we should convert the coordinate quantities in Eq (\ref{12}) into physical quantities.

@@

\subsection{Defining local quantities}

\subsubsection{Energy of shell}

There is a natural choice of what physical quantity we should use to replace $\Delta M$ with and that is the $tt$ component of the surface stress energy tensor, $S_{ab}$, of the shell as computed by the IJC

\begin{equation}
	S^a_b =  [K^a_b] - [K]h^a_b
\end{equation}

where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric we are using, $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature taken with respect to the induced metric and the notation of square brackets represents the difference in a quantity in two different induced metrics. 
%
%We can define the induced metrics for constant $r$ values; for region $I$ it is 
%
%\begin{equation}
%	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
%\end{equation}
%
%Analogously we have the metric corresponding to mass $M' = M- \Delta M$ in region $II$
%
%\begin{equation}
%	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
%\end{equation}
%
%We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same. Therefore it is easy to find a relation between the two time coordinates
%
%\begin{equation}
%	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
%\end{equation}
%
%Using this, we calculate the extrinsic curvature components
%
%\begin{eqnarray}
%	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
%	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
%	= (K^\phi_\phi)^{(M)}	\label{16}
%\end{eqnarray}
%
%where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$. Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).

The $tt$ component of the surface stress energy tensor is

\begin{equation}
	\sigma = S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{sig}
\end{equation}

>>>>

\begin{itemize}
\item {\bf Classical coherence by tracking geodesics.} The classical mode of a massless field basically has its peaks and nodes following null geodesics.
Thus, instead of actually solving the mode function, we can perform a much simpler calculation to track geodesics.
We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
\item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
A classical uncertainty can be expressed as deviation from such metric, $\Delta g_{\mu\nu}$. 
There are two major challenges here.
\begin{enumerate}
\item There are many more variables than the double-slit experiment. 
We consider only one particular form of $\Delta g_{\mu\nu}$ in this paper---back-reactions from the presence of extra matter of zero total energy. 
It is simple to calculate and reflects the physcial intuition of vacuum pair fluctuation.
\item The value of $\Delta g_{\mu\nu}$ is gauge dependent. 
By relating it to the presence of extra matter, we can express it as a gauge-invariant local quantity, which is the natural thing to hold fixed in our analysis.
\end{enumerate}
Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example. However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that. Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
\item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on renormalization.
\end{itemize}

@@

\begin{figure}[tb]
\begin{center}
\includegraphics[scale = 0.6]{Propertime.pdf}
\caption{The two parts of this diagrams describe two different scenarios. The trajectories of the photon are the lines in orange. The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines. The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$. The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$. Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively. The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
\label{fig-setup}
\end{center}
\end{figure}

After some formal calculations in the appendix \ref{Dtime}, we arrive at this simple expression:
\begin{equation}
\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = 
\left(\sqrt{\frac{r_2-2M}{r_1-2M}}\sqrt{\frac{r_1-2(M+\Delta M)}{r_2-2(M+\Delta M)}}-1\right)~,
\label{eq-result}
\end{equation}
where $r_1$ is the location of the inner shell, $r_2$ is the location of the outer shell, and $\pm\Delta M$ are their individual ADM masses.

@@

\textbf{XXX I-Sheng: Add a sentence about why we are using this limit?}

We can expand Eq (\ref{eq-result}) in the limit that $r_1>> \Delta M$ and $r_1>> \Delta r = r_2 - r_1$

\begin{equation}
	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \frac{\Delta M \Delta r}{(r_1-2M)^2}	\label{lim-result}
\end{equation}

This expression can be evaluated in three limits; 1) The Minkowski limit ($M=0$), 2) Far from horizon ($M <<r_1$), 3) Near horizon limit ($r_1<<M$). These limits have to be calculated using physical, local quantities, which are the local surface energy of the shell $\sigma$ and the proper distances. The calculations are performed in appendix \ref{finalEq} and the results are summarized below:

\begin{equation}
\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \begin{cases}
 \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
- 4\pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) & \ \ \ \ \ (M<<r_1)	\\
- 64 \pi  \sigma \Delta l \frac{M^2}{l^2} & \ \ \ \ \ (M>>r_1).
\end{cases}	\label{fin-result}
\end{equation}

Lets try to interpret each of these terms.

\begin{itemize}

\item \textbf{Minkowski limit ($M=0$)}: This seems to be a reasonable answer. 
First of all, it is quite unlikely that the entire shell of mass $\Delta M$ fluctuates out of vacuum.
It is reasonable that any change to the null geodesics is about a local energy density of the particular piece of shell they happen to pass through.
Secondly, this result is gauge invariant. For an observer at rest, $\sigma$ is the local energy density and $\Delta r$ is the proper distance. 
For a boosted observer, $\sigma$ increases by a boost factor while $\Delta r$ contracts by the same factor.
We take it as a good sign that other forms of geometric uncertainty can also be parametrize by a similar, gauge invariant quantity.

The na\"ive interpretation of the $M=0$ result is that even in Minkowski space, geometric uncertainty can potentially decohere classical mode functions.
By our definition, that poses some threat to QFT in Minkowski space.
We are going to assume that unitarity in QFT is fine in Minkowski space, effectively ``renormalize away'' the effect at $M=0$.
One can imagine a simple subtraction by a counter term.
Or alternatively, since the actual value of $(\sigma\Delta r)$ is unknown, we assume that it is small enough to not cause any concern.

\item \textbf{Far from horizon ($M<<r_1$)}: This is a region where we expect to understand the physics well. Indeed the QFT we test here on earth can be considered an example of this limit. If we keep $l$ fixed and along with the gauge invariant $\sigma \Delta l$, we see that the effect grows with $M$. Of course, we cannot assume that this grows without bound since we have to maintain the $M<<r_1$ limit. It is interesting to note that similar behaviour is observed when this limit no longer holds and this is what we describe next.

\item \textbf{Near horizon ($M>>r_1$)}: We can see that the same gauge-invariant quantity in Minkowski space from the $M=0$ limit appears here. We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} \rightarrow \infty$, which is the largest possible effect in the arrival times of two geodesics. However, the small $l$ limit may not be the best way to appreciate how this limit poses a threat to QFT. 
After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
The best way to understand this limit is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
However, the problem is that this effect grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.

\end{itemize}

%In that limit, Eq.~(\ref{eq-result}) can be approximated by
%\begin{equation}
%	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.	\label{eq-NearHorizon}
%\end{equation}
%where $l$ is the proper distance between $r_1$ and the horizon and $\delta l$ is the proper distance between the two shells. 
%We can see that the same gauge-invariant quantity in Minkowski space from Eq. (\ref{eq-Mink}) appears in the denominator this time
%\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\delta l$.}. We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} = -1$, which is the largest possible effect in the arrival times of two geodesics. However, the small $l$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT. 
%After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
%The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
%By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
%However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
%Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.

@@

Showing the lack of unitarity in the propagation of Hawking quanta does not resolve all the problems. 
Usually, one pictures a nonunitarity process as losing information. 
In the context of black hole information, a Hawking quantum actually has to {\it recover} information. 
A near-horizon mode starts from a maximally mixed (thermal) state with no information, since its partner is the interior mode that never comes out of the horizon. 
After the nonunitarity propagation to become an asymptotic Hawking quantum, it has to carry information to purify the rest of the Hawking radiation there.

Since unitarity is lost to the local geometric uncertainty, what restores information must be the interaction with the local geometry. 
An abstract realization of this information-recovery process is recently demonstrated in \cite{OsuPag16}. 
In order for local geometry to give this information to the Hawking quanta, it must first carry such information.
If was first suggested that superpositions of different classical geometries can store such information \cite{NomVar12}.
In the conventional picture, classical geometries are determined by only a few parameters such as the location and size of the black hole.
Thus the major objection to such picture is that the superpositions of classical geometries do not form a large enough Hilbert space to hold the required information.
Recently, it was realized that there are actually a much larger number of classical geometries differed by their soft hairs \cite{HawPer16}.
A simple counting suggested that the size of Hilbert space seems no longer the problem, so one should pursue this line of thoughts even further.

Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.

@@

\section{Calculation of proper time change}\label{Dtime}

\subsection{Background spacetime - no shell}

@@

\subsection{Perturbed spacetime - double shell}

Now we introduce two shells of matter with equal and opposite ADM mass, $\Delta M$ and $-\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}. We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells. In this case the particle's move through two different spacetime regions. Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M+\Delta M$ as shown in the top part of figure \ref{fig-setup}.
\\
\\
As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$. Now we need to find the corresponding coordinate time interval in region $II$, $\delta \hat{t}_1$ (in general we will use hats on top of quantities that are evaluated in region $II$). To do this we simply note that the corresponding proper time at $r_1$, $\delta \tau_1$ must be the same in both regions of spacetime - this is a simple consequence of the IJC. The coordinate time intervals at $r_1$, in the two different regions, are therefore related by

\begin{equation}
	\delta t_1 = \delta t_0 = \left( \frac{1 - \frac{2(M + \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta \hat{t}_1.
\end{equation}

@@

\begin{equation}
	\delta \hat{t}_2 = \delta \hat{t}_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M + \Delta M)}{r_2}} \right) \delta t_2.	\label{7}
\end{equation}

Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M + \Delta M)} \right) \right)^\frac{1}{2}$. Where we have dropped the $\left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$ term since we assume the observer is very far away. $\delta t_e = \delta \bar{\tau_0}$ when the observer is far away therefore we can define a dimensionless quantity that quantifies the change in proper time intervals for consecutive photons in perturbed spacetime case and the unperturbed case,

\begin{equation}
	 \frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M+\Delta M)} \right)^\frac{1}{2} - 1\right).	\label{10}
\end{equation}

This shows that when there are no shells, $\Delta M = 0$, there is no change in proper time intervals which is what one would expect.

\subsection{Leading order expansion limit}

By assuming $r_1>> \Delta r \equiv r_2 - r_1$ and $r_1>> \Delta M$ we can expand Eq (\ref{eq-result}), to leading order in small quantities,

\begin{eqnarray}
	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} & = & \left( \left( 1+ \frac{\Delta r}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{2\Delta M}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{\Delta r + 2 \Delta M}{r_1 - 2M} \right)^{-\frac{1}{2}} - 1	\nonumber	\\
	%& = & \left( 1 + \frac{1}{2} \frac{\Delta r}{r_1 - 2M} - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 \right) \left( 1 + \frac{\Delta M}{r_1 - 2M} - \frac{1}{2} \left(\frac{\Delta M}{r_1 - 2M} \right)^2 \right) \left( 1 - \frac{1}{2} \frac{\Delta r+ 2 \Delta M}{r_1 - 2M} + \frac{3}{8} \frac{(\Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} \right) - 1	\nonumber	\\
	%& = & \left( 1 + \frac{1}{2} \frac{\Delta r + 2 \Delta M}{r_1 - 2M} - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 + \frac{1}{2} \frac{\Delta r \Delta M}{(r_1 - 2M)^2} - \frac{1}{2} \left( \frac{\Delta M}{r_1 - 2M} \right)^2 \right) \left( 1 - \frac{1}{2} \frac{\Delta r + 2\Delta M}{r_1 - 2M} + \frac{3}{8} \frac{(\Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} \right) -1 \nonumber	\\
	& = & - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 + \frac{1}{2} \frac{\Delta r \Delta M}{(r_1 - 2M)^2} - \frac{1}{2} \left( \frac{\Delta M}{r_1 - 2M} \right)^2 - \frac{1}{4} \frac{( \Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} + \frac{3}{8} \frac{(\Delta r+ 2 \Delta M)^2}{(r_1 - 2M)^2} 	\nonumber	\\
	& = & \frac{\Delta M \Delta r}{(r_1 - 2M)^2}.
\end{eqnarray}

@@

\section{Deriving Eq (\ref{fin-result})}\label{finalEq}

The first step in this derivation is write down the physical, local, quantities needed to replace $\Delta M, r_1$ and $\Delta r$. The natural thing to replace $\Delta M$ is the surface stress energy, $\sigma$, of the shell. This is given by the $tt$ component of the surface stress energy tensor $S_{ab}$ given by the IJC.

%As the first step, we set $M=0$ in Eq.~(\ref{lim-result}) to study its meaning in Minkowski space,
%
%\begin{equation}
%\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx - \frac{\Delta M}{r_1^2} \Delta r 
%\equiv \sigma \Delta r~.	
%\label{eq-Mink}
%\end{equation}
%
%Next we study Eq.~(\ref{lim-result}) with an actual black hole. 
%Before we perform any analysis with a black hole it is important to convert the coordinate quantities in Eq (\ref{lim-result}) to physical quantities. We implicitly did this in the Minkowski limit; the variables in Eq (\ref{eq-Mink}) indeed represent the physical surface energy of the shell and the proper distance to it. In the case of a black hole we have to be more careful. The natural quantity to use for the local surface energy of the shell is the time component of the surface stress energy term, $S_{ab}$, given by the IJC

\begin{equation}
	S^a_b = [K^a_b] - [K]h^a_b,
\end{equation}

where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric, $h^{ab}$, we are using. $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature.
We can define the induced metrics for constant $r$ values; for region $I$ it is

\begin{equation}
	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
\end{equation}

Analogously we have the metric corresponding to mass $M' = M+ \Delta M$ in region $II$

\begin{equation}
	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
\end{equation}

We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same. Therefore it is easy to find a relation between the two time coordinates

\begin{equation}
	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
\end{equation}

Using this, we calculate the extrinsic curvature components

\begin{eqnarray}
	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
	= (K^\phi_\phi)^{(M)}	\label{16}
\end{eqnarray}

where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$. Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
 The time component of the surface stress energy tensor $S^0_0$ is

\begin{equation}
	\sigma = S^0_0 = \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2(M+\Delta M)}{r_1} \right)^\frac{1}{2} \right).
\end{equation}

This expression represents a small change in the mass and thus can be written as

\begin{eqnarray}
	\sigma & = & \frac{1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M. \nonumber	\\
	& = &  \frac{\Delta M}{4 \pi r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}}.	\label{sig-Dm}
\end{eqnarray}

Next we need to replace the coordinate distance $\Delta r$ with the proper distance $\Delta l$ and the relation between them is given by

\begin{equation}
	\Delta l = \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} \Delta r.	\label{Dl-Dr}
\end{equation}
